Reaction-diffusion spacial modeling of COVID-19 in Chicago

### 2021-08-26 pres-8-27/slides/work-04.tex
SoReMo updates

\begin{slide}{Current Work}
	\begin{table}[h]
		\centering
		\caption{ODE parameters for Chicago: optimal (best-fitting), median and interquartile range, and variation range used in the optimization algorithm. Initial parameter guesses were uniformly sampled within these ranges.}
		\label{tab:parameters}
		\begin{tabular}{ c c c c }
			\hline
			\hline
			&	&	Median (interquartile range)	&	Initial value \\
			\hline
			Population	&	$N$	&	2,695,598	& \\
			Initial population	&	$(I_0, R_0)$	&	(127, 2)	& \\
			Transmission rate, $S \rightarrow I$ [per day]	&	$\beta$\footnote{The transmission rate $\beta$ must be divided by $N$ when used in the ODE model.}	&	0.38206(0.38204-0.38209)	&	$c \in U[0,1]$ \\
			Transition rate, $I \rightarrow R$ [per day]	&	$\gamma$	&	 0.39656(0.39654-0.39659)	&	$c \in U[0.25,0.75]$ \\
			\hline
			\hline
		\end{tabular}
	\end{table}
\end{slide}

>>>>

\begin{slide}{Current Work}
	{\large \textbf{ODE Results}} \\

	\vspace{.5cm}

	Data were obtained from the Chicago Data Portal. \\
	Optimal ODE model parameters obtained from 1,000 optimizations (implemented in MATLAB). \\

	\vspace{.3cm}

	\begin{table}[h]
		\centering
		\label{tab:parameters}
		\begin{tabular}{ c c c c }
			\hline
			\hline
			&	&	Median (interquartile range)	&	Initial value \\
			\hline
			Population	&	$N$	&	2,695,598	& \\
			Initial population	&	$(I_0, R_0)$	&	(127, 2)	& \\
			Transmission rate, $S \rightarrow I$ [per day]	&	$\beta$	&	0.38206(0.38204-0.38209)	&	$c \in U[0,1]$ \\
			Transition rate, $I \rightarrow R$ [per day]	&	$\gamma$	&	 0.39656(0.39654-0.39659)	&	$c \in U[0.25,0.75]$ \\
			\hline
			\hline
		\end{tabular}
	\end{table}

	Note the transmission rate $\beta$ must be divided by $N$ when used in the ODE model.
\end{slide}
